Interval Probability for Fuzzy Quantum Theories

### 2016-05-28 prob.tex
Remove the citation which are not directly used...

In a strict computational or experimental setting, one may question
the reliance of the definition of probability space on the uncountable
and uncomputable real interval $[0,1]$. This interval includes numbers
like $0.h_1h_2h_3\ldots$ where $h_i$ is 1 or 0 depending on whether
Turing machine $M_i$ halts or not. Such numbers cannot be
computed. This interval also includes numbers like $\frac{\pi}{4}$
which can only be computed with increasingly large resources as the
precision increases.
% \yutsung{Check the meaning of the ``computing $\frac{\pi}{4}$'', because
% Bailey Borwein Plouffe formula can computing the $n$th binary digit of $\pi$ 
% using base 16 directly.}
Therefore, in a resource-aware computational or experimental setting,
it is more appropriate to consider probability measures that map
events to a set of elements computable with a fixed set of
resources. We expand on this observation and then consider
%% two approaches from the literature: set-valued probability
%% measures~\cite{Artstein1972,PuriRalescu1983} and 
interval-valued probability
measures~\cite{Dempster1967,Shafer1976,Weichselberger2000,JamisonLodwick2004}
in detail.\footnote{There is another possible approach that can be
  used to split the real interval $[0,1]$ into a collection of
  subsets~\cite{Artstein1972,PuriRalescu1983} \amr{need to explain the
    connection and why we are not using it.}}

>>>>

In a strict computational or experimental setting, one may question
the reliance of the definition of probability space on the uncountable
and uncomputable real interval $[0,1]$. This interval includes numbers
like $0.h_1h_2h_3\ldots$ where $h_i$ is 1 or 0 depending on whether
Turing machine $M_i$ halts or not. Such numbers cannot be
computed. This interval also includes numbers like $\frac{\pi}{4}$
which can only be computed with increasingly large resources as the
precision increases.
% \yutsung{Check the meaning of the ``computing $\frac{\pi}{4}$'', because
% Bailey Borwein Plouffe formula can computing the $n$th binary digit of $\pi$ 
% using base 16 directly.}
Therefore, in a resource-aware computational or experimental setting,
it is more appropriate to consider probability measures that map
events to a set of elements computable with a fixed set of
resources. We expand on this observation and then consider
%% two approaches from the literature: set-valued probability
%% measures~\cite{Artstein1972,PuriRalescu1983} and 
interval-valued probability
measures~\cite{Dempster1967,Shafer1976,JamisonLodwick2004}
in detail.\footnote{There is another possible approach that can be
  used to split the real interval $[0,1]$ into a collection of
  subsets~\cite{PuriRalescu1983} \amr{need to explain the
    connection and why we are not using it.}}
